Stack Safety as a Security Property

### 2020-07-10 main.tex
Nits on 2

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
What is stack safety? Numerous mechanisms have been proposed to guard
against attacks that corrupt the call stacks of running programs,
\ifaftersubmission
and many
others rely on a protected stack as an assumption to provide higher level
guarantees\bcp{this is a good point, but we don't pick it up anywhere in the
  paper, do we?}\leo{No, should we delete this? it still makes sense in flow}
\bcp{Let's delete for now; later, we can try to incorporate it in the body
  of the paper.}
\fi,
but a clear and precise definition of stack safety is missing
from the literature.
%
We propose a formal definition phrased in the technical
terminology of language-based security---as a combination of a
confidentiality property (callees should not be able to read their caller's
stack frames) and an integrity property (callees should not corrupt their
caller's stack frames or control state).
  %
We discuss how these properties are enforced or approximated by
existing stack protection mechanisms and describe some useful
stronger and weaker variants.  \ifaftersubmission\bcp{should we mention stktokens here?}
\leo{Not sure. We almost never cite stuff in the abstract, do we?}\fi
\end{abstract}

@@

Enforcement mechanisms are modeled as {\em policies} that add some auxiliary
policy state to the ordinary machine state
%\bcp{This may be surprising to people who are not thinking about micropolicies.\apt{added para below}}
and a partial policy step function that refines the machine step
function by allowing or disallowing a step to be taken based on its
auxiliary state.  Enforcement works by halting the program before it
can perform an action that would violate the security property; our
properties are naturally therefore \emph{termination insensitive.}
This model will be made more precise in \cref{sec:prelim}.

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
What is stack safety? Numerous mechanisms have been proposed to guard
against attacks that corrupt the call stacks of running programs,
\ifaftersubmission
and many
others rely on a protected stack as an assumption to provide higher level
guarantees,\bcp{this is a good point, but we don't pick it up anywhere in the
  paper, do we?}\leo{No, should we delete this? it still makes sense in flow}
\bcp{Let's delete for now; later, we can try to incorporate it in the body
  of the paper.}
\fi
but a clear and precise definition of stack safety is missing
from the literature.
%
We propose a formal definition phrased in the technical
terminology of language-based security---as a combination of a
confidentiality property (callees should not be able to read their caller's
stack frames) and an integrity property (callees should not corrupt their
caller's stack frames or control state).
  %
We discuss how these properties are enforced or approximated by
existing stack protection mechanisms and describe some useful
stronger and weaker variants.  \ifaftersubmission\bcp{should we mention stktokens here?}
\leo{Not sure. We almost never cite stuff in the abstract, do we?}\fi
\end{abstract}

@@

Enforcement mechanisms are modeled as {\em policies} that add some auxiliary
policy state to the ordinary machine state
%\bcp{This may be surprising to people who are not thinking about micropolicies.\apt{added para below}}
and a partial policy step function that refines the machine step
function by allowing or disallowing a step to be taken based on its
auxiliary state.  Enforcement works by halting the program before it
can perform an action that would violate the security property; our
properties are therefore naturally \emph{termination insensitive.}
This model will be made more precise in \cref{sec:prelim}.
